Put Title here

### 2018-11-21 General WLD combinatorics.tex
actually get rid of that commented out fragment

\note{This was commented out in the file: some (old?) version of the inductive argument?}
such that $b+1 \in V_{p_1}$, with an endpoint more clockwise on $W$ than the endpoint of $p$ supported by $b+1$: see Figure~\ref{fig:base step of alg induction}.

\begin{figure}
\begin{tikzpicture}[rotate=15]
\begin{scope}
\drawWLD{12}{2}
\drawprop{3}{2}{10}{2} % P
% number vertices a,a+1,b,b+1 for prop P

% clip these
\drawprop{3}{-2}{12}{-2}
\drawprop{2}{0}{12}{2}
\drawprop{6}{0}{10}{-2} % p1

\end{scope}
\end{tikzpicture}
\caption{Base step: if $P$ survives $n$ steps of the algorithm, there must be another propagator $p_1$ to its right on edge $(b,b+1)$.}
\label{fig:base step of alg induction}
\end{figure}

The propagator $p_1$ forms the base step for the following induction:

Suppose that $p_r$ is a propagator supported on $(i,i+1,m,m+1)$ and removed at step $m+1$ of the algorithm; we will show that there must also be a propagator $p_{r+1}$ supported on $(i',i'+1,m',m'+1)$ with $i \leq i'$ and $m \geq m'$, which is removed at step $m'+1$.  Since we can't have both $i' = i$ and $m'=m$, $p_{r+1}$ bounds a region containing strictly fewer vertices than $p_r$.

Notice that if we restrict our attention to the region bounded by $p_r$ and the edges of the diagram from $i$ to $m+1$, then propagators outside of this region can affect the algorithm only at vertices $i$, $i+1$.  (The starting vertex 1 lies outside this region, by assumption.)

Given a propagator $p_r$ supported on $(i,i+1,m,m+1)$ and removed at step $m+1$, we must also have a propagator $q$ to its right which is removed at step $m$ (``protecting'' $p_r$ at step $m$).  This splits into two cases:

\textbf{Case I}: If $q$ is supported on $(k,k+1,m-1,m)$ for some $k \geq i$, then $p_{r+1}:=q$  satisfies the conditions of the induction step.

\textbf{Case II}: Suppose $q$ is supported on $(k,k+1,m,m+1)$ for some $k$; since the diagram is admissible, we have $k > i$.  In particular, anything that happens at vertex $k+1$ is unaffected by propagators outside the region bounded by $p_r$, since $k+1 > i+1$.  But $q$ must survive until step $m$, so there must be another propagator $q'$ to the right of $q$, which protects $q$ at step $k+1$.  The admissibility of $W$ implies that $q'$ is supported on $(j,j+1,k,k+1)$ for some $j \geq i$, and we can take $p_{r+1}:=q'$.

\begin{figure}
\begin{tabular}{ccc}
\begin{tikzpicture}[rotate=15]
\begin{scope}
\drawWLD{12}{2}
\drawprop{3}{0}{10}{0} % p_r
% number vertices i,i+1,m,m+1

%clip these
\drawprop{6}{0}{9}{0} % q
\end{scope}
\end{tikzpicture}

& \qquad \qquad &
\begin{tikzpicture}[rotate=15]
\begin{scope}
\drawWLD{12}{2}
\drawprop{3}{0}{10}{2} % p_r
% number vertices i, i+1, m, m+1

\drawprop{7}{2}{10}{-2} %q
% vertices k,k+1, m,m+1

% clip this one
\drawprop{4}{0}{7}{-2} % q'
% vertices j,j+1,k, k+1

\end{scope}
\end{tikzpicture}
\\
Case I & & Case II
\end{tabular}

\caption{Inductive step: if propagator $q$ is removed at step $m$, then it lies on either edge $(m-1,m)$ (Case I) or $(m,m+1)$ (Case II).}
\label{fig: cases for inductive step, algorithm}
\end{figure}

By induction, we will eventually find a propagator on a region with 3 or fewer vertices, which is inadmissible.

\note{end of the piece that was commented out in the file}

>>>>

%such that $b+1 \in V_{p_1}$, with an endpoint more clockwise on $W$ than the endpoint of $p$ supported by $b+1$: see Figure~\ref{fig:base step of alg induction}.
%
%\begin{figure}
%\begin{tikzpicture}[rotate=15]
%\begin{scope}
%\drawWLD{12}{2}
%\drawprop{3}{2}{10}{2} % P
%% number vertices a,a+1,b,b+1 for prop P
%
%% clip these
%\drawprop{3}{-2}{12}{-2}
%\drawprop{2}{0}{12}{2}
%\drawprop{6}{0}{10}{-2} % p1
%
%
%\end{scope}
%\end{tikzpicture}
%\caption{Base step: if $P$ survives $n$ steps of the algorithm, there must be another propagator $p_1$ to its right on edge $(b,b+1)$.}
%\label{fig:base step of alg induction}
%\end{figure}
%
%The propagator $p_1$ forms the base step for the following induction:
%
%Suppose that $p_r$ is a propagator supported on $(i,i+1,m,m+1)$ and removed at step $m+1$ of the algorithm; we will show that there must also be a propagator $p_{r+1}$ supported on $(i',i'+1,m',m'+1)$ with $i \leq i'$ and $m \geq m'$, which is removed at step $m'+1$.  Since we can't have both $i' = i$ and $m'=m$, $p_{r+1}$ bounds a region containing strictly fewer vertices than $p_r$.
%
%Notice that if we restrict our attention to the region bounded by $p_r$ and the edges of the diagram from $i$ to $m+1$, then propagators outside of this region can affect the algorithm only at vertices $i$, $i+1$.  (The starting vertex 1 lies outside this region, by assumption.)
%
%Given a propagator $p_r$ supported on $(i,i+1,m,m+1)$ and removed at step $m+1$, we must also have a propagator $q$ to its right which is removed at step $m$ (``protecting'' $p_r$ at step $m$).  This splits into two cases:
%
%\textbf{Case I}: If $q$ is supported on $(k,k+1,m-1,m)$ for some $k \geq i$, then $p_{r+1}:=q$  satisfies the conditions of the induction step.
%
%\textbf{Case II}: Suppose $q$ is supported on $(k,k+1,m,m+1)$ for some $k$; since the diagram is admissible, we have $k > i$.  In particular, anything that happens at vertex $k+1$ is unaffected by propagators outside the region bounded by $p_r$, since $k+1 > i+1$.  But $q$ must survive until step $m$, so there must be another propagator $q'$ to the right of $q$, which protects $q$ at step $k+1$.  The admissibility of $W$ implies that $q'$ is supported on $(j,j+1,k,k+1)$ for some $j \geq i$, and we can take $p_{r+1}:=q'$.
%
%\begin{figure}
%\begin{tabular}{ccc}
%\begin{tikzpicture}[rotate=15]
%\begin{scope}
%\drawWLD{12}{2}
%\drawprop{3}{0}{10}{0} % p_r
%% number vertices i,i+1,m,m+1
%
%%clip these
%\drawprop{6}{0}{9}{0} % q
%\end{scope}
%\end{tikzpicture}
%
%& \qquad \qquad &
%\begin{tikzpicture}[rotate=15]
%\begin{scope}
%\drawWLD{12}{2}
%\drawprop{3}{0}{10}{2} % p_r
%% number vertices i, i+1, m, m+1
%
%\drawprop{7}{2}{10}{-2} %q
%% vertices k,k+1, m,m+1
%
%% clip this one
%\drawprop{4}{0}{7}{-2} % q'
%% vertices j,j+1,k, k+1
%
%\end{scope}
%\end{tikzpicture}
%\\
%Case I & & Case II
%\end{tabular}
%
%\caption{Inductive step: if propagator $q$ is removed at step $m$, then it lies on either edge $(m-1,m)$ (Case I) or $(m,m+1)$ (Case II).}
%\label{fig: cases for inductive step, algorithm}
%\end{figure}
%
%By induction, we will eventually find a propagator on a region with 3 or fewer v%ertices, which is inadmissible.
